A Plasma Torus Around a Young Low-Mass Star

### 2025-03-18 paper/ms.tex
update ms

%\subsection{Introduction}
M dwarfs, stars with masses below about half that of the Sun, are the
only type of star to offer near-term prospects for detecting the
atmospheres of rocky exoplanets with surface water
\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  How
an M dwarf's evolution influences its planets---especially the
retention of their atmospheres--- has concurrently become a major
theme in exoplanet and stellar astrophysics.  Previous work has
established that most M dwarfs host close-in planets
\cite{Dressing2015} that are often subject to long
circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
radiation \cite{France2013}, and to a high incidence of flares and
coronal mass ejections \cite{Gunther2020}.  Nevertheless, despite excellent
work in these areas, the properties of the plasma and magnetospheric
environments that bathe young, close-in exoplanets have remained
challenging to quantify.

@@

The two leading hypotheses to explain the CPVs are either that
transiting clumps of circumstellar material corotate with the star
\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars represent
an extreme in naturally-occurring distributions of starspots or faculae
\cite{Koen2021}.  
% TODO: might want to plug Shapiro, Seager, ACC dark faculae...
While the main argument against a starspot-only explanation invokes the
timescales and amplitudes of the sharpest photometric features, no
independent evidence has yet been acquired for the presence of any
circumstellar material.  Geometrically, transiting clumps would imply an
occurrence a few to at most ten times the observed rate.  Such clumps
could therefore exist around 10-30\% of M dwarfs during their early
lives.

@@

In this study, we present the first observations of corotating clumps of
cool plasma around a CPV.  We identified TIC~141146667 in previous work
\cite{Bouma2024} by searching the TESS two-minute data \cite{Ricker2015}
for stars showing at least three sharp and periodic dips per cycle.  We
selected the star for spectroscopy because its brightness and rapid
rotation offer sensitivity to small variations in the line profiles.  We
observed for five hours on 17~February~2024 (UT) using the High
Resolution Echelle Spectrometer (HIRES; \cite{vogt_hires_1994}) on the
Keck I 10m telescope.  TESS observed the star over a four week period
from 30~January~2024 to 26~February~2024 with a duty cycle of 77\%.
During the spectral observations, TESS was performing a data downlink;
TESS data collection resumed 12 hours (three rotation cycles) after the
spectra were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
detailed photometric behavior of the star before and after the exact
epoch of observation; the photometric morphology is similar before and
after the data gap.

@@

% photometry
Figure~\ref{fig:spec} shows the data from February 2024.  Over
timescales of years, CPVs maintain a fixed period while their
photometric morphology evolves.  TIC~141146667 indeed evolved relative
to the February 2022 discovery data \cite{Bouma2024}.  In the February
2024 TESS data, the average photometric signal showed a small brightening
over 45\% of the period, followed by a complex flux dip spanning 55\%
of the period.  This eclipse feature shows two to three local
photometric minima, and one to two local maxima.  Its W-shape is
suggestive of eclipse geometries seen in some forward models of warped
plasma tori \cite{Townsend2008}.

@@

These sinusoidal emission features require circumstellar clumps of
partially-ionized hydrogen to be corotating with the star.  
Based on its period, this material's motion is not Keplerian; it can
only be explained by plasma being dragged along with the rotating
stellar magnetic field. 
The velocity semi-amplitude of the sinusoids then gives the distance
of the clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
closer clump, and 3.9\,$R_\star$ for the other.   These clumps transit
in front of the star when passing from negative to positive velocity.
This implies that the spectroscopic transit of the 2.1-2.7\,$R_\star$
clump occurs simultaneously with the sharp photometric spike visible
in the TESS data.

@@

The material's composition -- either pure plasma, or else a dusty plasma
-- can be clarified by time-series optical and infrared
spectrophotometry.  While observations of CPVs in the optical have
previously suggested chromaticity consistent with dust
\cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such as
electron scattering in a plasma transiting over starspots might also
produce chromatic features \cite{Rackham2018}.  The composition and size
distribution of any dust that is present would be most easily resolved
by measuring the extinction curve for one or more CPVs from
1-10\,$\mu$m.  Composition and size distributions similar to debris from
rocky bodies seen around white dwarfs \cite{Reach2009} would indicate a
rocky-body origin.  Compositions and sizes to the ISM would be
indicative of condensed dust in an M dwarf wind, similar to that formed
in the environments of more evolved stars \cite{Marigo2008}.

The role of the star's magnetic field could be better understood through
new observations, and new theory.  From the theoretical perspective,
there is an urgent need for rigid-field (magneto)-hydrodynamic modeling
to go beyond previous work \cite{Townsend2005,Townsend2008} and to
explore the effects of non-dipolar field contributions.  In particular,
dynamo simulations of fully-convective M dwarfs have suggested that
global-scale mean fields might be confined to a single hemisphere
\cite{Brown2020}; such fields could yield accumulation surfaces quite
different from those that have previously been explored
\cite{Townsend2008}.  Observationally, spectropolarimetry has the
potential to assess both the field strength and topology.  An
independent probe could also be connected the recent work
\cite{Kaur2024} showing that CPVs are variable radio emitters with
emission components that can be both persistent, and also short-lived
and highly polarized.  In particular, detecting radio emission produced
by an electron cyclotron maser instability would provide a measurement
of the field strength at the site of the emitting region.

It is currently unclear what, if any, relationship CPVs have to the
close-in exoplanets that exist around most M dwarfs \cite{Dressing2015}.
However, 0.3-3\% of young M dwarfs show the CPV phenomenon
\cite{Rebull2020}, and our data show that the phenomenon occurs when
clumps of circumstellar material transit the star.  The implied
geometric correction suggests that an appreciable minority (10-30\%) of
young M dwarfs -- the rapidly rotating ones with centrifugal
magnetospheres -- host similar circumstellar environments to the CPVs.

@@

Broadly, Figure~\ref{fig:fulllc} shows that a large, complex eclipse
feature was present before and after the HIRES data were
acquired.  From BTJD 3352~-~3356, this eclipse had two sharp local
minima;  the local minimum at $\phi$$\approx$0.8 disappeared following
the flare at BTJD 3353, yielding an eclipse more closely resembling a
long ``V'' than a ``W''.  Similar state changes have previously been
noted and discussed \cite{Stauffer2017,Bouma2024}.  The photometric
shape therefore evolved during the twelve cycles spanning the
3356~-~3358 gap, since the average shape from 3358-3363 more
closely resembles the initial ``W''.

@@

{\it No Evidence For Binarity}---Any significant periodicity in the
radial velocity time-series is ruled out at the rotation period for
semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This sets
an upper limit on the mass of any putative companion at the four hour
period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
companions at wider separations, the Gaia DR3 renormalized unit weight
error (RUWE), a proxy for the goodness of fit for a single-source
astrometric model to the Gaia astrometry, is 1.23, within the usual
range for apparently single sources.  There are no resolved sources in
the Gaia DR3 point source catalog.  Finally, we checked the TESS light
curve for evidence of secondary photometric periods by subtracting the
mean CPV signal over each sector and performing a phase-dispersion
minimization analysis \cite{Stellingwerf1978,2021zndo...1011188B}.
There were no secondary periods in the TESS data.  Previous work
\cite{Bouma2024} has shown that about 30\% of CPVs show evidence for
excess noise above the Gaia single-source astrometric model, and about
40\% of CPVs show evidence for unresolved binary companions based on the
presence of secondary photometric periods.  This agrees with analyses
showing that multi-periodic low-mass stars are generally unresolved
binaries \cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
consistent with that for field M dwarfs \cite{Winters2019}, pointing to
a weak or non-existent connection between the CPV phenomenon and
binarity.  For TIC~141146667 specifically, while we find no evidence for
stellar multiplicity, our data are minimally constraining for the
scenario of a low-luminosity companion ($F_1$/$F_2$$\lesssim$0.1) at
large orbital separations.

@@

{\it Effective temperature, radius, mass, and spectral type} We adopted
the star's effective temperature and radius measured using the spectral
energy distribution (SED) fitting procedure described by
\cite{Bouma2024}.  To summarize, this approach used
\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
solar abundances and the \cite{Barber2006} water line lists.  This
approach fitted for the stellar effective temperature, radius,
reddening, surface gravity, metallicity, and distance by comparing the
measured broadband magnitudes against pre-computed model grids.
Specifically, we performed the fit using the broadband magnitudes from
Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the most
constraining power for the star's effective temperature (2972 $\pm$
40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
metallicity, and reddening are typically only weakly constrained.  We
determined the star's spectral type to be M5.5Ve by visually comparing
the HIRES spectra against the photometric standards tabulated by
\cite{Bochanski2007}, which agrees with the effective temperature from
the SED fitting \cite{Pecaut2013}.

@@

{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has found that over 90\% of CPVs are associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is in the minority.  We calculated the probability of
TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  That particular model
classifies it as a field star at $>$99.9\% confidence.  We also searched
the local vicinity of TIC~141146667 for neighbors with similar projected
on-sky velocities using \texttt{comove} \cite{Tofflemire2021}.  This
yielded no strong candidates for co-moving stars with projected
tangential velocities $\Delta v_{\rm T}$$<$5\,\kms that share its
isochronal youth.

@@

Despite uncertainties in the details, what can be stated with confidence
is that lithium is not abundant in the spectrum of TIC~141146667.
Figure~\ref{fig:liew_population} compares our upper limit against the
equivalent width measurements reported by \cite{Jeffries2023}
based on the Gaia-ESO spectroscopic survey.  If the star were
$\lesssim$20\,Myr old, at its temperature we would expect to see
lithium in abundance ($>$400\,m\AA).  Since we do not, we can set an
empirical bound on the lithium-derived age of $t_{\rm
Li,emp}$$\gtrsim$20\,Myr.  The \cite{Feiden2016} lithium isochrones
provide a point for theoretical comparison, and suggest that since
$M_{\rm K}$$\approx$6.67\,mag, $t_{\rm Li,th}$$\gtrsim$35\,Myr is the
theoretical age at which complete depletion occurs in a star with this
luminosity (see e.g.~Figure 7 from \cite{Wood2023}).

@@

The full HIRES coverage spans 3650-7960\,\AA, and variable
  emission is visible in Balmer lines from $n$=10$\rightarrow$2, Ca[H]
  and Ca[K], the Mg[I] b triplet, and the 5875 He[I] emission line.

Ha
Hgamma
Hdelta?
He5875
CaK
K7700
Li6708

%TODO: add figure showing spectral variability!

\subsection{Spectral Behavior of Other Lines}

First, chromospheric:

{\it H$\gamma$, H$\delta$}
Line ratios.

{\it Ca [K]}
{\it Also} shows some high-velocity emission.  So, the emitting material has
calcium ions.

{\it He 5880}
Also variable...

{\it Magnesium b orders}
Shows some variability that is horrendously blended.

{\it K[I] 7700}
Literally the only obvious photospheric line.

>>>>

%\subsection{Introduction}
M dwarfs, stars with masses below about half that of the Sun, are the
only type of star to offer near-term prospects for detecting the
atmospheres of rocky exoplanets with surface water
\cite{NAP26141}.  Investment with JWST has proceeded accordingly.  How
an M dwarf's evolution influences its planets---especially the
retention of their atmospheres--- has concurrently become a major
theme in exoplanet and stellar astrophysics.  Previous work has
established that most M dwarfs host close-in planets
\cite{Dressing2015} that are often subject to long
circumstellar disk lifetimes \cite{Ribas2015}, to large doses of UV
radiation \cite{France2013}, and to a high incidence of flares and
coronal mass ejections \cite{Gunther2020}.  However, despite excellent
work in these areas, the properties of the plasma and magnetospheric
environments that bathe young, close-in exoplanets have remained
challenging to quantify.

@@

The two leading hypotheses to explain the CPVs are either that
transiting clumps of circumstellar material corotate with the star
\cite{Stauffer2017,Gunther2022,Bouma2024}, or that these stars represent
an extreme in naturally-occurring distributions of starspots or faculae
\cite{Koen2021}.  
% TODO: might want to plug Shapiro, Seager, ACC dark faculae...
While the main argument against a starspot-only explanation invokes the
timescales and amplitudes of the sharpest photometric features, no
independent evidence has yet been acquired for the presence of any
circumstellar material.  Geometrically, transiting clumps would imply an
occurrence a few to at most ten times the observed rate.  The clumps
could therefore exist around 10-30\% of M dwarfs during their early
lives.

@@

In this study, we present the first observations of corotating clumps of
cool plasma around a CPV.  We identified TIC~141146667 in previous work
\cite{Bouma2024} by searching the TESS two-minute data \cite{Ricker2015}
for stars showing at least three sharp, periodic dips per cycle.  We
selected the star for spectroscopy because its brightness and rapid
rotation enable efficiently studying small variations in the line profiles.  We
observed for five hours on 17~February~2024 (UT) using the High
Resolution Echelle Spectrometer (HIRES; \cite{vogt_hires_1994}) on the
Keck I 10m telescope.  TESS observed the star over a four week period
from 30~January~2024 to 26~February~2024 with a duty cycle of 77\%.
During the spectral observations, TESS was performing a data downlink;
TESS data collection resumed 12 hours (three rotation cycles) after the
spectra were acquired.  Extended Data Figure~\ref{fig:fulllc} shows the
detailed photometric behavior of the star before and after the exact
epoch of observation; the photometric morphology is similar before and
after the data gap.

@@

% photometry
Figure~\ref{fig:spec} shows the data from February 2024.  Over
timescales of years, CPVs maintain a fixed period while their
photometric morphology evolves.  TIC~141146667 indeed evolved relative
to the February 2022 discovery data \cite{Bouma2024}.  In February
2024, the average photometric signal showed a small brightening
over 45\% of the period, followed by a complex flux dip spanning 55\%
of the period.  This eclipse feature shows two to three local
photometric minima, and one to two local maxima.  Its W-shape is
suggestive of eclipse geometries seen in some forward models of warped
plasma tori \cite{Townsend2008}.

@@

These sinusoidal emission features require circumstellar clumps of
partially-ionized hydrogen to corotate with the star.  
Based on the period, this material's motion is not Keplerian; it can
only be explained by plasma being dragged along with the rotating
stellar magnetic field. 
The velocity semi-amplitude of the sinusoids then gives the distance
of the clumps from the stellar surface: 2.1-2.7\,$R_\star$ for the
closer clump, and 3.9\,$R_\star$ for the other.   These clumps transit
in front of the star when passing from negative to positive velocity.
This implies that the spectroscopic transit of the 2.1-2.7\,$R_\star$
clump occurs simultaneously with the sharp photometric spike visible
in the TESS data.

@@

The material's composition -- either pure plasma, or else a dusty plasma
-- can be clarified by time-series optical and infrared
spectrophotometry.  While observations of CPVs in the optical have
previously suggested chromaticity consistent with dust
\cite{Tanimoto2020,Gunther2022,Koen2023}, a gray opacity source such as
electron scattering in a plasma transiting over starspots might also
produce chromatic features \cite{Rackham2018}.  The composition and size
distribution of any dust that is present could be determined
by measuring the extinction curve for one or more CPVs from
1-10\,$\mu$m.  Composition and size distributions similar to debris from
rocky bodies seen around white dwarfs \cite{Reach2009} would indicate a
rocky-body origin.  Compositions and sizes similar to the ISM would be
indicative of condensed dust in an M dwarf wind, similar to that formed
in the environments of more evolved stars \cite{Marigo2008}.

The role of the star's magnetic field could be better understood through
new observations, and new theory.  From the theoretical perspective,
there is an urgent need for rigid-field (magneto)-hydrodynamic modeling
to go beyond previous work \cite{Townsend2005,Townsend2008} and to
explore the effects of non-dipolar field contributions.  In particular,
dynamo simulations of fully-convective M dwarfs have suggested that
global-scale mean fields might be confined to a single hemisphere
\cite{Brown2020}; such fields could yield accumulation surfaces quite
different from those that have previously been explored
\cite{Townsend2008}.  Observationally, spectropolarimetry has the
potential to assess both the field strength and topology.  An
independent probe could also be connected the recent work
\cite{Kaur2024} showing that CPVs are variable radio emitters with
emission components that can be not only persistent, but also
short-lived and highly polarized.  In particular, detecting radio
emission produced by an electron cyclotron maser instability
\cite{Callingham2021} would provide a measurement of the field
strength at the site of the emitting region.

It is currently unclear what, if any, relationship CPVs have to the
close-in rocky exoplanets that exist around most M dwarfs \cite{Dressing2015}.
However, 0.3-3\% of young M dwarfs show the CPV phenomenon
\cite{Rebull2020}, and our data show that the phenomenon occurs when
clumps of circumstellar material transit the star.  The implied
geometric correction suggests that an appreciable minority (10-30\%) of
young M dwarfs -- the rapidly rotating ones with centrifugal
magnetospheres -- host similar circumstellar environments to the CPVs.

@@

Figure~\ref{fig:fulllc} shows that a large, complex eclipse
feature was present before and after the HIRES data were
acquired.  From BTJD 3352~-~3356, this eclipse had two sharp local
minima;  the local minimum at $\phi$$\approx$0.8 disappeared following
the flare at BTJD 3353, yielding an eclipse more closely resembling a
long ``V'' than a ``W''.  Similar state changes have previously been
noted and discussed \cite{Stauffer2017,Bouma2024}.  The photometric
shape therefore evolved during the twelve cycles spanning the
3356~-~3358 gap, since the average shape from 3358-3363 more
closely resembles the initial ``W''.

@@

{\it No Evidence For Binarity}---Any significant periodicity in the
radial velocity time-series is ruled out at the rotation period for
semi-amplitudes above 2.85\,\kms\ (at 3$\sigma$ confidence).  This sets
an upper limit on the mass of any putative companion at the four hour
period of $m \sin i $$<$2.4\,$M_{\rm Jup}$.  Regarding possible
companions at wider separations, the Gaia DR3 renormalized unit weight
error (RUWE), a proxy for the goodness of fit for a single-source
astrometric model to the Gaia astrometry, is 1.23, within the usual
range for apparently single sources.  There are no resolved sources in
the Gaia DR3 point source catalog.  Finally, we checked the TESS light
curve for evidence of secondary photometric periods by subtracting the
mean CPV signal over each sector and performing a phase-dispersion
minimization analysis \cite{Stellingwerf1978,2021zndo...1011188B}.
There were no secondary periods in the TESS data.  Previous work
\cite{Bouma2024} has shown that about 30\% of CPVs show evidence for
excess noise above the Gaia single-source astrometric model, and about
40\% of CPVs show evidence for unresolved binary companions based on the
presence of secondary photometric periods.  This agrees with analyses
showing that multi-periodic low-mass stars are generally unresolved
binaries \cite{Tokovinin2018}.  Overall, the CPV binary fraction seems
consistent with that for field M dwarfs \cite{Winters2019}, pointing to
a weak or non-existent connection between the CPV phenomenon and
(wide) binarity.  For TIC~141146667 specifically, while we find no evidence for
stellar multiplicity, our data are minimally constraining for the
scenario of a low-luminosity companion ($F_1$/$F_2$$\lesssim$0.1) at
with apparent separations below 0$\farcs$1.

@@

{\it Effective temperature, radius, mass, and spectral type} We adopted
the star's effective temperature and radius measured using the spectral
energy distribution (SED) fitting procedure described by
\cite{Bouma2024}.  To summarize, this approach used
\texttt{astroARIADNE} \cite{Vines2022} with the BT-Settl stellar
atmosphere models \cite{Allard2012}, assuming the \cite{Asplund2009}
solar abundances and the \cite{Barber2006} water line lists.  This
approach fitted for the stellar effective temperature, radius,
reddening, surface gravity, metallicity, and distance by comparing the
measured broadband magnitudes against pre-computed model grids.
Specifically, we performed the fit using the broadband magnitudes from
Gaia DR2, APASS, 2MASS, SDSS, and WISE $W1$ and $W2$.  The resulting
best-fit SED is shown in Figure~\ref{fig:sed}.  This method has the most
constraining power for the star's effective temperature (2972 $\pm$
40\,K) and radius (0.42 $\pm$ 0.02\,$R_\odot$); the surface gravity,
metallicity, and reddening are only weakly constrained.  We
determined the star's spectral type to be M5.5Ve by visually comparing
the HIRES spectra against the photometric standards tabulated by
\cite{Bochanski2007}.   This result agrees with the effective
temperature found from the SED fitting \cite{Pecaut2013}.

@@

{\it Age: No Obvious Association Membership}---Previous work
\cite{Bouma2024} has found that over 90\% of CPVs are associated with
known young moving groups based on their positions and kinematics.
TIC~141146667 is in the minority.  We calculated the probability of
TIC~141146667 being part of any of the nearby known groups using
BANYAN\,$\Sigma$ v1.2 \cite{Gagne2018}.  That particular model
classifies it as a field star at $>$99.9\% confidence.  We also searched
the local vicinity of TIC~141146667 for neighbors with similar projected
on-sky velocities using \texttt{comove} \cite{Tofflemire2021}.  This
yielded no strong candidates for co-moving stars with projected
tangential velocities $\Delta v_{\rm T}$$<$5\,\kms\ that share its
isochronal youth.

@@

Despite uncertainties in the details, what can be stated with confidence
is that lithium is not abundant in the spectrum of TIC~141146667.
Figure~\ref{fig:liew_population} compares our upper limit against the
equivalent width measurements reported by \cite{Jeffries2023}
based on the Gaia-ESO spectroscopic survey; Figure~\ref{fig:hirescuts}
shows the associated raw spectra.  If the star were $\lesssim$20\,Myr
old, at its temperature we would expect to see lithium in abundance
($>$400\,m\AA).  Since we do not, we can set an empirical bound on the
lithium-derived age of $t_{\rm Li,emp}$$\gtrsim$20\,Myr.  The
\cite{Feiden2016} lithium isochrones provide a point for theoretical
comparison, and suggest that since $M_{\rm K}$$\approx$6.67\,mag,
$t_{\rm Li,th}$$\gtrsim$35\,Myr is the theoretical age at which
complete depletion occurs in a star with this luminosity (see
e.g.~Figure 7 from \cite{Wood2023}).

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=\textwidth]{figures/sf5.pdf}
  \caption{Time evolution of select regions in the Keck/HIRES
  spectra from 17 February 2025.
  The horizontal axis shows $\Delta v \equiv c (\lambda -
  \lambda_0)/\lambda_0$, the relative velocity centered on each line's
  rest wavelength, normalized by the stellar equatorial velocity.
  }
  \label{fig:hirescuts}
\end{figure}

Figure~\ref{fig:hirescuts} shows a few regions of interest in the HIRES
spectra, which cover 3650-7960\,\AA.
Higher order Balmer lines including H$\gamma$ and H$\delta$ (the
$n=5\rightarrow2$ and $n=6\rightarrow2$ transitions respectively) do
show some variability outside the line core.
However, this variability is not clearly periodic in the
same manner as the emission seen in H$\alpha$.
This could be because there are insufficient hydrogen ions in the
relevant excited states, or due to the lower precision of the spectra
in these bluer regions.
The Ca HK doublet for instance is also detectable in emission, however
the continuum near it is not.
Chromospheric emission lines in the magnesium triplet order are
also detectable, but sufficiently blended to be rendered unusable.

One notable feature is that H$\alpha$, H$\gamma$, H$\delta$, and He
5876\,\AA\ all show a blue excess at $\phi$$\approx$0.2.  At the same
epoch, only H$\alpha$ clearly shows a resolved red excess as well,
although $H\gamma$ and H$\delta$ are broader at this time.  Given the
sudden rise of this emission in $<$15\,minutes, and the association
between He 5876\,\AA\ and stellar outflows at high excitation energy,
this component of the spectra might be more easily associated with a
flare than with a stable, periodic component.

Finally, the Li\,\textsc{I} 6708\,\AA\ doublet, which shows no obvious
absorption, as well as the broad K\,\textsc{I} 7699\,\AA\ feature are
both shown in Figure~\ref{fig:hirescuts}.  In the latter, narrow
telluric absorption features overlap the blue wing of the line.
Neither of these regions shows any notable variability.

%\subsection{Spectral Behavior of Other Lines}
%
%First, chromospheric:
%
%{\it H$\gamma$, H$\delta$}
%Line ratios.
%
%{\it Ca [K]}
%{\it Also} shows some high-velocity emission.  So, the emitting material has
%calcium ions.
%
%{\it He 5880}
%Also variable...
%
%{\it Magnesium b orders}
%Shows some variability that is horrendously blended.
%
%{\it K[I] 7700}
%Literally the only obvious photospheric line.
